\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-27 paper.qmd
Updated Figure 4 rectangle

```{r}
#| label: fig-two-curvy-true-proj
#| fig-cap: "Two views of the true model (blue lines) in $2\\text{-}D$ projections from $7\\text{-}D$, for the two-curvy data (black points). The data is spread along the non-linear shaped clusters, and does not vary much from the curves. The **langevitour** software is used to view the data with a tour, and the full video is available at <>." 
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5

@@

```{r}
#| label: fig-NLDR-two-curvy
#| echo: false
#| fig-cap: "Key steps for constructing the model on the UMAP layout ($k=2$): (a) data, (b) hexagon bins, (c) bin centroids, and (d) triangulated centroids. The S-curve data is shown."
#| fig-width: 12
#| fig-height: 4
#| out-width: 100%

@@

# To move the rectangle to ignore the overlap with the centroids
rect_adj <- tibble(x1 = 0.03, x2 = 0.03)

@@

    annotate("text", x=-0.18, y=-0.22, 

>>>>

```{r}
#| label: fig-two-curvy-true-proj
#| fig-cap: "Two views of the true model (blue lines) in $2\\text{-}D$ projections from $7\\text{-}D$, for the two-curvy clusters data (black points). The data is spread along the non-linear shaped clusters, and does not vary much from the curves. The **langevitour** software is used to view the data with a tour, and the full video is available at <>." 
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5

@@

```{r}
#| label: fig-NLDR-two-curvy
#| echo: false
#| fig-cap: "Key steps for constructing the model on the UMAP layout ($k=2$): (a) data, (b) hexagon bins, (c) bin centroids, and (d) triangulated centroids. The two-curvy clusters data is shown."
#| fig-width: 12
#| fig-height: 4
#| out-width: 100%

@@

# To move the rectangle to ignore the overlap with the centroids
# rect_adj <- tibble(x1 = 0.03, x2 = 0.03)
rect_adj <- tibble(x1 = -0.03, x2 = 0.03)

@@

    annotate("text", x=-0.18, y=-0.24, 

### 2024-09-27 paper.tex
Updated Figure 4 rectangle

\caption{\label{fig-two-curvy-true-proj}Two views of the true model
(blue lines) in \(2\text{-}D\) projections from \(7\text{-}D\), for the
two-curvy data (black points). The data is spread along the non-linear
shaped clusters, and does not vary much from the curves. The
\textbf{langevitour} software is used to view the data with a tour, and
the full video is available at \textless\textgreater.}

@@

\caption{\label{fig-NLDR-two-curvy}Key steps for constructing the model
on the UMAP layout (\(k=2\)): (a) data, (b) hexagon bins, (c) bin
centroids, and (d) triangulated centroids. The S-curve data is shown.}

>>>>

\caption{\label{fig-two-curvy-true-proj}Two views of the true model
(blue lines) in \(2\text{-}D\) projections from \(7\text{-}D\), for the
two-curvy clusters data (black points). The data is spread along the
non-linear shaped clusters, and does not vary much from the curves. The
\textbf{langevitour} software is used to view the data with a tour, and
the full video is available at \textless\textgreater.}

@@

\caption{\label{fig-NLDR-two-curvy}Key steps for constructing the model
on the UMAP layout (\(k=2\)): (a) data, (b) hexagon bins, (c) bin
centroids, and (d) triangulated centroids. The two-curvy clusters data
is shown.}
